LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives

### 2025-05-05 paper/paper.tex
paper: et al citations

Several recent studies have explored the use of Large Language Models (LLMs) for knowledge graph generation. Xu et al \cite{xu2024chattf} utilize a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from textual data about Chinese traditional folklore. Beyond the cultural heritage domain, Van Cauter and Yakovets \cite{cauter2024ontology} demonstrate KG generation from maintenance short texts, while Carriero et al \cite{carriero2025humanevaluationofprocedural} construct KGs from procedural texts such as recipes or manuals. These studies often experiment with different prompting strategies to optimize the extraction process. In particular, Iga et al \cite{iga2024assessllm} demonstrate the impact of well-crafted prompts, specifically those employing in-context learning and chain-of-thought techniques, in yielding significant improvements. This highlights the importance of effective prompting methodologies to guide LLMs to generate accurate and consistent knowledge graphs aligned with a given ontology.

Our research focuses on the extraction of knowledge graphs from museum archives using an ontology derived from the CIDOC-CRM. Unlike the two-stage prompting approach employed by \cite{xu2024chattf}, we explore the effectiveness of a single-stage prompting method. Moreover, our study incorporates a comprehensive evaluation strategy that includes both intrinsic (ontology conformance) and extrinsic (KBQA task) metrics.

>>>>

Several recent studies have explored the use of Large Language Models (LLMs) for knowledge graph generation. Xu et al. \cite{xu2024chattf} utilize a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from textual data about Chinese traditional folklore. Beyond the cultural heritage domain, Van Cauter and Yakovets \cite{cauter2024ontology} demonstrate KG generation from maintenance short texts, while Carriero et al. \cite{carriero2025humanevaluationofprocedural} construct KGs from procedural texts such as recipes or manuals. These studies often experiment with different prompting strategies to optimize the extraction process. In particular, Iga et al. \cite{iga2024assessllm} demonstrate the impact of well-crafted prompts, specifically those employing in-context learning and chain-of-thought techniques, in yielding significant improvements. This highlights the importance of effective prompting methodologies to guide LLMs to generate accurate and consistent knowledge graphs aligned with a given ontology.

Our research focuses on the extraction of knowledge graphs from museum archives using an ontology derived from the CIDOC-CRM. Unlike the two-stage prompting approach employed by Xu et al. \cite{xu2024chattf}, we explore the effectiveness of a single-stage prompting method. Moreover, our study incorporates a comprehensive evaluation strategy that includes both intrinsic (ontology conformance) and extrinsic (KBQA task) metrics.
